A Cross-Benchmark Comparison of 87 Learning to Rank Methods

### 2015-05-05 paper/IPM/paper.tex
nieuw werk

\begin{document}
\begin{frontmatter}
\title{A Cross-Benchmark Comparison of 87 Learning to Rank Methods}
\author[avanade,ut]{Niek Tax\corref{cor}\fnref{fn}}
\ead{niek.tax@avanade.com}
\author[avanade]{Sander Bockting}
\ead{sander.bockting@avanade.com}
\author[ut]{Djoerd Hiemstra}
\ead{d.hiemstra@utwente.nl}
\cortext[cor]{Corresponding Author: Niek Tax, Avanade Netherlands B.V., Versterkerstraat 6,
1322AP Almere, the Netherlands; Email, niek.tax@avanade.com; Phone, +31634085760}
\fntext[fn]{Author is affiliated with the University of Twente, but this paper was written during his stay at Avanade Netherlands B.V.}
\address[avanade]{Avanade Netherlands B.V., Versterkerstraat 6,
1322AP Almere, the Netherlands}
\address[ut]{University of Twente, P.O. Box 217, 7500AE Enschede,
the Netherlands}
\begin{abstract}
Learning to rank is an increasingly important scientific field that comprises the use of machine learning for the ranking task. New learning to rank methods are generally evaluated on benchmark test collections. However, comparison of learning to rank methods based on evaluation results is hindered by non-existence of a standard set of evaluation benchmark collections. In this paper we propose a way to compare learning to rank methods based on a sparse set of evaluation results on a set of benchmark datasets. Our comparison methodology consists of two components: 1) Normalized Winning Number, which gives insight in the ranking accuracy of the learning to rank method, and 2) Ideal Winning Number, which gives insight in the degree of certainty concerning its ranking accuracy. Evaluation results of 87 learning to rank methods on 20 well-known benchmark datasets are collected through a structured literature search. ListNet, SmoothRank, FenchelRank, FSMRank, LRUF and LARF are the best performing learning to rank methods in increasing order of Normalized Winning Number and decreasing order of Ideal Winning Number.
\end{abstract}
\begin{keyword}
Learning to rank \sep Information retrieval \sep Evaluation metric
\end{keyword}
\end{frontmatter}

>>>>

\begin{document}
\begin{frontmatter}
\title{A Cross-Benchmark Comparison of 87 Learning to Rank Methods}
\author[avanade,tue]{Niek Tax\corref{cor}\fnref{fn}}
\ead{n.tax@tue.nl}
\author[avanade]{Sander Bockting}
\ead{sander.bockting@avanade.com}
\author[ut]{Djoerd Hiemstra}
\ead{d.hiemstra@utwente.nl}
\cortext[cor]{Corresponding Author: Niek Tax, Eindhoven University of Technology, Department of Mathematics and Computer Science, P.O. Box 513, 5600MB Eindhoven, the Netherlands; Email, n.tax@tue.nl; Phone, +31634085760}
\fntext[fn]{Author is affiliated with Eindhoven University of Technology, but this paper was written during his stay at Avanade Netherlands B.V.}
\address[avanade]{Avanade Netherlands B.V., Versterkerstraat 6,
1322AP Almere, the Netherlands}
\address[ut]{University of Twente, P.O. Box 217, 7500AE Enschede,
the Netherlands}
\address[tue]{Eindhoven University of Technology, P.O. Box 513, 5600MB Eindhoven, the Netherlands}
\begin{abstract}
Learning to rank is an increasingly important scientific field that comprises the use of machine learning for the ranking task. New learning to rank methods are generally evaluated on benchmark test collections. However, comparison of learning to rank methods based on evaluation results is hindered by non-existence of a standard set of evaluation benchmark collections. In this paper we propose a way to compare learning to rank methods based on a sparse set of evaluation results on a set of benchmark datasets. Our comparison methodology consists of two components: 1) Normalized Winning Number, which gives insight in the ranking accuracy of the learning to rank method, and 2) Ideal Winning Number, which gives insight in the degree of certainty concerning its ranking accuracy. Evaluation results of 87 learning to rank methods on 20 well-known benchmark datasets are collected through a structured literature search. ListNet, SmoothRank, FenchelRank, FSMRank, LRUF and LARF are the best performing learning to rank methods in increasing order of Normalized Winning Number and decreasing order of Ideal Winning Number.
\end{abstract}
\begin{keyword}
Learning to rank \sep Information retrieval \sep Evaluation metric
\end{keyword}
\end{frontmatter}
